Product graphics

### 2009-05-14 product-graphics.tex
Some ideas for continuous plots

@@

The three plots above are special cases of $a(i, j) = w(i, j)^x * h(i, j)^y$.  $x + y = 1$.

@@

Impossible to simultaneously satisfy all constraints.  Every product plot requires the creator to trade off between these.

@@

\section{Connection with log-linear models}
\label{sec:models}

which imply the obvious mapping between d(i, j) and a(i, j).  For >2d,
the definitions generalise in the obvious, but the constraints become
more complicated.

$log(d(i,j)) = 1 + d_{i \cdot} + d_{j|i}$
$log(d(i,j)) = 1 + d_{\cdot j} + d_{i|j}$

>>>>

Give a few examples of non-traditional continuous-categorical plots.  Fluctuation diagram for exploring joint 2d distribution.  Mosaic for conditional.  Age and year distribution.

Cat + continuous.

@@

@@

Impossible to simultaneously satisfy all constraints.  Every product plot requires the creator to trade off between these.  We will focus our attention on rectangular partitions.  Special cases of $a(i, j) = w(i, j)^x * h(i, j)^y$,   $x + y = 1$.

@@

\section{Connection with log-linear models}
